An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-24 draft.tex
Marble diagram notation explained

The controller is an essential component of the architecture (Figure \ref{fig:kafkEO})
because it is responsible for maintaining the evolutionary loop. It takes newly
evolved populations from the Output Queue, mixes them,   and produces new
messages from the result. At the same time, it must keep track of two conditions
for ending the loop: the number of messages it has received reaches a maximum
value, or the error of the best solution goes below a specific threshold.  Finally, it
must filter out remnant messages from other experients. Messages from other
experiments can remain in the queues because of the asynchronous nature of the
system.  We chose to implement the controller in Python but using an API
specialized in asynchronous event-driven programming over data streams.  The
open-source library is called Reactive Extensions for Python (RxPY)
\url{https://github.com/ReactiveX/RxPY}an it is based on the Observer pattern
\cite{gamma1995design} and functional programming.

>>>>

The controller is an essential component of the architecture (Figure \ref{fig:kafkEO})
because it is responsible for maintaining the evolutionary loop. It takes newly
evolved populations from the Output Queue, mixes them,   and produces new
messages from the result. At the same time, it must keep track of two conditions
for ending the loop: the number of messages it has received reaches a maximum
value, or the error of the best solution goes below a specific threshold.  Finally, it
must filter out remnant messages from other experients. Messages from other
experiments can remain in the queues because of the asynchronous nature of the
system.  We chose to implement the controller in Python but using an API
specialized in asynchronous event-driven programming over data streams.  
The open-source library is called Reactive Extensions (ReactiveX) for Python 
\url{https://github.com/ReactiveX/RxPY} an it is based on the Observer 
pattern \cite{gamma1995design} and functional programming.

In ReactiveX, an observer object subscribes to an Observable. Observables emit a
sequence of items, and all the subscribed observers react to each emission. The
ReactiveX library includes several reactive operators that we can use to
transform and combine sequences of items. These operators provide reactive
extensions that allow us to compose asynchronous sequences together in a
declarative manner. In Figure /ref{marble}, we use a so-called marble diagram to
represent the composition of Observables and reactive extensions operators. We
represent the timeline of an Observable as a horizontal arrow, which indicates
that time flows from left to right. In the diagram, items are represented as
marbles. The position of each marble indicates the point in time when they were
emitted by the Observable. Reactive operators are represented as text boxes,
showing the transformation to be applied. Normally, a transformation results in
another Observable, again emitting the results.
